\documentclass[a4paper]{scrartcl}
%alternatives to classic article are: book, report, scrartcl (recommended), scrreprt, scrbook
%more options Optionen: 11pt, 12pt, twoside, twocolumn

\usepackage[english]{babel}  %for German texts: ngerman
%\usepackage[utf8]{inputenc}   %encode in UTF-8 (I think TexStudio does this by default)


\usepackage{flafter} % figures always BELOW respective section headers
\usepackage[bottom]{footmisc}

% citations and bibliography
\usepackage[backend = biber,citestyle=authoryear, bibstyle = authoryear, uniquename=false, uniquelist=false, doi=false,isbn=false,eprint=false]{biblatex}

\AtEveryBibitem{ % clears appendix
	\clearlist{language} 
	\clearfield{urlyear}
	\clearfield{urldate}
	\clearfield{month}
	\clearfield{labelmonth}
} 

\renewbibmacro{in:}{}

\usepackage{xpatch}

% No dot before number of articles
\xpatchbibmacro{volume+number+eid}{%
	\setunit*{\adddot}%
}{%
}{}{}

% Number of articles in parentheses
\DeclareFieldFormat[article]{number}{\mkbibparens{#1}}


\addbibresource{zotero_refs.bib} %pass the name of the bib file


% define glossary
\usepackage[nopostdot,nogroupskip,style=super,nonumberlist,automake]{glossaries}

\glstocfalse
\makeglossaries

\newglossaryentry{mdp}{name={MDP},description={Markov Decision Process}}
\newglossaryentry{fem}{name={FEM},description={Feature Extraction Method}}
\newglossaryentry{td_error}{name={TD error},description={temporal-difference error}}


%Formatting and Layout
\usepackage[left = 4cm, right = 2cm, top = 2.5cm, bottom = 2cm]{geometry}

% line spacing: 1.5
\usepackage[onehalfspacing]{setspace}
\renewcommand{\baselinestretch}{1.5}

%no indentation in captions of figures and tables
\setcapindent{0pt} 


% Package for algorithm boxes
\usepackage{algorithm,algorithmic}

% section name is printed on the head of each page
\pagestyle{headings}   


\usepackage{graphicx}  %for graphics
\usepackage{amsmath,amsfonts,amssymb,amsthm,mathtools}  %math packages



% abstract and appendices
\usepackage{abstract}
\usepackage[title]{appendix}
\newcommand*{\Appendixautorefname}{appendix}

%References
\usepackage[hidelinks]{hyperref}
\usepackage{cleveref}


\begin{document}
	
	% overwrite autoreference labels
	\def\sectionautorefname{section}
	\def\subsectionautorefname{section}
	\def\subsubsectionautorefname{section}
	\def\equationautorefname{equation}
	\def\algorithmautorefname{Algorithm}
	

	
	% start roman page numbers
	\pagenumbering{Roman}
	
	% center front page, no page number
	\newgeometry{left = 2cm, right = 2cm}
	\thispagestyle{empty}
	
	\begin{titlepage}
		\centering
		\vspace{1cm}
		{\Large\bfseries Collusion among autonomous pricing algorithms utilizing function approximation methods\par}
		\vspace{4cm}
		{\large\itshape Heinrich-Heine-University Düsseldorf\par}
		\vspace{0.5cm}
		{\large\itshape Düsseldorf Institute for Competition Economics (DICE)\par}
		\vspace{0.5cm}
		{\large\itshape Prof. Dr. Hans-Theo Normann\par}
		\vspace{0.5cm}
		{\large\itshape Summer Term 2021\par}
		{\large\itshape \par}
		\vfill
		by\par
		\vspace{0.2cm}
		Malte Jeschonneck\\
		Malte.Jechonneck@uni-duesseldorf.de\\
		Mobile: 01575-1294972\\
		Matriculation Number: 2307497\\
		Mörsenbroicher Weg 179, 40470 Düsseldorf\\
		Program: Economics, M. Sc.\\
		
		
		
		\vfill
		
		% Bottom of the page
		{\large Submitted: \today\par}
	\end{titlepage}

\restoregeometry % go back to default layout

\newpage
	\begin{abstract}
		 The increased prevalence of pricing algorithms incited an ongoing debate about new forms of collusion. The concern is that intelligent algorithms may be able to forge collusive schemes without being explicitly instructed to do so. I attempt to examine the ability of \emph{reinforcement learning} algorithms to maintain collusive prices in a simulated oligopoly of price competition. To my knowledge, this study is the first to use a reinforcement learning system with linear function approximation and eligibility traces in an economic environment. I show that the deployed agents sustain supra-competitive prices, but tend to be exploitable by deviating agents in the short-term. The price level upon convergence crucially hinges on the utilized method to estimate the qualities of actions. These findings are robust to variations of parameters that control the learning process and the environment.
	\end{abstract}
	
\newpage	
	
	% TOC, LOF, LOT, Abbreviations
	\tableofcontents
	\newpage
	\listoffigures
	\newpage
	\listoftables
	\newpage
	\printglossary[title={List of Abbreviations}] %Generate List of Abbreviations
	\newpage
	\pagenumbering{arabic}
	
	\input{01_introduction.tex}
	
	\input{02_literature.tex}
	
	\input{03_environment.tex}
	
	\input{04_algorithm.tex}
	
	\input{05_feature_extraction.tex}
	
	\input{06_results.tex}
	
	\input{07_extensions.tex}
	
	\input{08_conclusions.tex}

	\clearpage
	\printbibliography
	\clearpage
	
	\begin{appendices}
	\section{Further Results}\label{appendix}
	
		\input{99_appendix.tex}
	
	\clearpage
	
	\section{Further Variations}\label{appendix_2}

		\input{999_appendix_2}
	\end{appendices}
\end{document}
